
# Importing data
```{r, echo=FALSE}
mydata=read.csv("C:\\Users\\user\\Desktop/GData.csv",header=T,sep=",")
head(mydata)
variable=c("Total","Goods","Services")
```

#### Mean,Median,Quartiles
```{r, echo=FALSE}
summary(mydata)
```


#### Variance,Std.Dev & Std.Error
```{r, echo=FALSE}
variable=c("Total","Goods","Services")
variance=c(1,2,3)
std.dev=c(1,2,3)
std.error=c(1,2,3)
for(i in 1:3)
{
  variance[i]=var(mydata[,i])
  std.dev[i]=sd(mydata[,i])
  std.error[i]=std.dev[i]/sqrt(length(mydata[,i]))
}

data.frame(variable,variance,std.dev,std.error)
```

#### Covariance matrix
```{r, echo=FALSE}

cov(mydata)


```
#### Correlation matrix
```{r, echo=FALSE}
cor(mydata)
```

#### Coefficient of Variation

```{r, echo=FALSE}
coeff_var=c(1,2,3)
for(i in 1:3)
{
coeff_var[i]=sd(mydata[,i])/mean(mydata[,i])*100
}
data.frame(cbind(variable,coeff_var))
```

#### Percentiles for "Goods"
```{r, echo=FALSE}
perc=seq(1,100,1)
for(i in 1:100)
{
perc[i]=quantile(mydata[,2],i*0.01)
}
perc


```


### Skewness & Kurtosis for all the variables

```{r, echo=FALSE}
library(moments)
skewness=c(1,2,3)
kurtosis=c(1,2,3)
for(i in 1:3)
{
skewness[i]=round(skewness(mydata[,i]),2)
kurtosis[i]=round(kurtosis(mydata[,i]),2)
}
data.frame(cbind(variable,skewness,kurtosis))
```


# Box plot 

```{r, echo=FALSE}
names=data.frame(c(names(mydata)))
par(mfrow=c(1,3))
for(i in 1:3)
{
boxplot(mydata[,i],main=names[i,1],col="gray")
}


```

# Histogram
```{r, echo=FALSE}

par(mfrow=c(1,3))
for(i in 1:3)
{
hist(mydata[,i],main=variable[i])
}
```

# Scatter Plot of "Goods" and "Services"

```{r, echo=FALSE}
library(car)
scatterplot(mydata[,2],mydata[,3],main="Scater plot of Goods and Services")
```


# Ogives of Goods

```{r, echo=FALSE}
a=mydata[,2]
n=8
d=seq(1,8,1)
for(i in 1:8)
{
d[i]=sum(ifelse(a>(i-1)*((max(a)-min(a))/n)+min(a) & a<=i*((max(a)-min(a))/n)+min(a),1,0))
}
e=cumsum(d)
plot(e,main="Ogives of Goods")
lines(e)

```

# combination of histogram, ogives and probability plot

```{r, echo=FALSE}
h=hist(a,breaks=7, col="gray",freq=T,include.lowest=T,main="Histogram,Ogives & Probability Plot of Goods")
xfit=seq(min(a),max(a),length=length(a)) 
yfit=dnorm(xfit,mean=mean(a),sd=sd(a)) 
yfit=yfit*diff(h$mids[1:2])*length(a) 
par(new = TRUE)
lines(xfit, yfit, col="blue", lwd=2,type="l")
d=seq(1,8,1)
v=((max(a)-min(a))/8)
for(i in 1:8)
{
d[i]=sum(ifelse(a>(i-1)*v+min(a)-1& a<=i*v+min(a),1,0))
}
e=cumsum(d)
par(new=T)
plot(e)
lines(e)

```

# Standardising the variable "Goods"
```{r, echo=FALSE}
z=(mydata[,2]-mean(mydata[,2]))/sd(mydata[,2])
round(z,3)
```

# Checking Normality of "Goods"
###Method 1: By Standardising the Variable
```{r, echo=FALSE}


parameter=rbind("mean","std.dev")
value=c(round(mean(z)),sd(z))
data.frame(parameter,value)

```

###Method 2: By using Q_Q Plot

```{r, echo=FALSE}
qqnorm(mydata[,2])

```


###Method 3: Normal Probability Plot for "Goods"

```{r, echo=FALSE}
a=mydata[,2]
h=hist(a,breaks=7, col="red",freq=T,include.lowest=T,main="Normal Probability plot for Goods")
xfit=seq(min(a),max(a),length=length(a)) 
yfit=dnorm(xfit,mean=mean(a),sd=sd(a)) 
yfit=yfit*diff(h$mids[1:2])*length(a) 
lines(xfit, yfit, col="blue", lwd=2,type="l")

```


###Method 4: Confidence Interval

```{r, echo=FALSE}

e=matrix(nrow=4,ncol=3)
e[1,]=c("1 sd","2 sd","3 sd")
for(i in 2:4)
{
a=mydata[,i-1]
for(j in 1:3)
{
e[i,j]=round(sum(ifelse(a<mean(a)+ j*sd(a) & a>mean(a)- j*sd(a),1,0))/length(a)*100,2)
}
}
variable=c("type","Total","Goods","Services")
data.frame(variable,e)
```
#Generating random numbers

```{r, echo=FALSE}
round(runif(100,1,200))

```

